\documentclass[letterpaper,9pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]


\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
  \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\
    \textit{\small #3} & \textit{\small #4} \\
  \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheadingEducation}[6]{
  \vspace{-1pt}\item
  \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\
    \textit{\small #3} & \textit{\small #4} \\
    \textit{\small #5} & \textit{\small #6} \\
  \end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \Large Ryan Gess & Email : gess.rmg@gmail.com\\
   medium.com/@gess.rmg & Mobile : +1-814-826-5808 \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheadingEducation
      {Carnegie Mellon University}{Pittsburgh, PA}
      {Master of Science, Electrical and Computer Engineering; 3.4/4}{Jan. 2022 -- May. 2023}
      {Bachelor of Science, Electrical and Computer Engineering; 3.3/4}{Aug. 2018 -- Dec. 2021}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Raytheon}{Colorado Springs, CO}
      {Senior Software Engineer}{Jan 2026 - Present}
      \resumeItemListStart
        \item
          Improved scalability and developer velocity by extracting coupled radar software into an independently buildable and testable services.
        \item
          Enable decomposed radar software to compile within \textbf{Docker} containers, improving build reproducibility across developer and CI environments.
        \item
          Diagnosed and resolved failing and flaky unit tests across \verb!C++! and \textbf{Ada} codebases, improving test reliability and accelerating integration timelines.
      \resumeItemListEnd
    \resumeSubheading
      {Collins Aerospace}{Colorado Springs, CO}
      {Software Engineer II}{Jul 2023 - Dec 2025}
      \resumeItemListStart
        \item
          Developed mission-critical \textbf{Java} features for ingesting and routing land and space-based sensor data supporting the C2BMC National Team.
        \item
          Designed and implemented \textbf{persistent, coherent storage} to maintain high availability of data across distributed system instances, improving system resiliency.
        \item
          Built an application integrity verification tool that reduced troubleshooting and deployment investigation time.
        \item
          Led a technical risk assessment for major technology upgrades and proposed mitigation strategies adopted by the team.
      \resumeItemListEnd

    \resumeSubheading
      {Collins Aerospace}{Colorado Springs, CO}
      {Software Engineer Intern}{Jun 2022 - Aug 2022}
      \resumeItemListStart
        \item
          Developed an automated testing application for verifying system requirements using \textbf{Java} on C2BMC National Team.
        \item
          Expanded automated test coverage by implementing new requirement tests and modernizing legacy tests for version compatibility.
        \item
          Planned and built new \textbf{Java/Maven} application for aggregating test results on web app to provide historical verification context.
      \resumeItemListEnd

    \resumeSubheading
      {Microsoft}{Redmond, WA}
      {Software Engineer Intern}{Jun 2021 - Aug 2021}
      \resumeItemListStart
        \item
          Optimized \textbf{Yocto} builds for an embedded Linux platform to improve developer productivity.
        \item
          Integrated ccache into the Yocto build pipeline, achieving a \textbf{1.2x} build speed improvement.
        \item
          Designed a parallelized unit test pipeline, reducing pull request turnaround time by \textbf{25\%}.
      \resumeItemListEnd

    \resumeSubheading
      {Parthean}{Pittsburgh, PA}
      {Full Stack Developer}{Jan 2020 - Jan 2021}
      \resumeItemListStart
        \item
          Built and designed an analytics page for educators of online learning platform using \textbf{React}, \textbf{D3.js}.
        \item
          Integrated quantitative metrics to capture member engagement and community growth.
        \item
          Restructured data model to allow extensibility and improve performance and efficiency.
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects \& Leadership}
  \resumeSubHeadingListStart
    \resumeSubItem{XDash}
      {Personalized real-time futures trading platform using \textbf{Go}, \textbf{React}, \textbf{Generative AI} and \textbf{ProjectX} API.}
    \resumeSubItem{Alpine Racing and Freestyle Team, Team Captain}
      {Lead team practices and fitness activities. Coordinate with competition leaders to plan events.}
  \resumeSubHeadingListEnd

%
%--------PROGRAMMING SKILLS------------
\section{Skills}
 \resumeSubHeadingListStart
   \resumeSubItem{Languages}{: C/C++, Python, Go, Java, JavaScript, SQL, Ada, Matlab}
   \resumeSubItem{Tools/Frameworks}{: AWS, React, Numpy, PyTorch, gdb, Django, Spring, Maven, Tailwind CSS}
   \resumeSubItem{Abilities}{: Data Analysis, Machine Learning, Binary Exploitation, Web Development, Decision Making}
   \resumeSubItem{Security Clearance}{Active DoD Secret}
 \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}